%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-2pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jun-Liang Chen} \\ \vspace{1pt}
    \faIcon{mobile-alt} \href{tel:886983116913}{{+886 983 116 913}} $|$
    \faIcon{envelope} \href{mailto:oren.ccl@gmail.com}{{oren.ccl@gmail.com}} $|$
    \faIcon{linkedin} \href{https://www.linkedin.com/in/jun-liang-chen-6a7743188/}{{junliangchen}} $|$
    \faIcon{github} \href{https://github.com/orenccl}{{orenccl}} $|$
    \faIcon{link} \href{https://orenccl.github.io/}{{https://orenccl.github.io/}}
\end{center}

\section{Summary}
\small{Software Engineer with 3+ years of experience in scalable web applications and interactive games. Expertise in Typescript, JavaScript, Vue.js, Unity, and NestJS. Passionate about open-source contributions and impactful software solutions.}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Taipei University of Technology}{Taipei, Taiwan}
      {Bachelor of Engineering in Electrical Engineering}{Sep. 2013 -- Jun 2017}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: Typescript, JavaScript, Python, Java, C/C++, Shell Script} \\
     \textbf{Frameworks}{: Vue.js, Unity, Node.js, Nest.js, Express.js, Spring Boot} \\
     \textbf{Technologies}{: Linux, MySQL, Redis, Podman, Nginx, Prometheus, Grafana} \\
      \textbf{DevOps Tools}{: Git, Docker, Podman, GitLab CI, GitHub Actions} \\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Jan. 2024 -- Present}
      {AI VALUE.,Ltd.}{Taipei, Taiwan}
      \resumeItemListStart
        \resumeItem{Developed a Vue.js-powered, game-based learning platform with a user-friendly, engaging interface.}
        \resumeItem{Built efficient, scalable back-end services using NestJS for optimized data handling and server performance.}
        \resumeItem{Implemented MikroORM to streamline database operations, ensuring seamless data integration and management.}
      \resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Engineer}{July 2023 -- Dec. 2023}
      {International Integrated Systems, Inc.}{Taipei, Taiwan}
      \resumeItemListStart
        \resumeItem{Maintained and upgraded an existing on-demand weather platform, enhancing its functionality using Spring Boot.}
        \resumeItem{Developed the Leisure Weather project’s front-end using Vue.js to enhance user experience.}
    \resumeItemListEnd

    \resumeSubheading
      {Game Developer}{Nov. 2021 -- Apr. 2023}
      {ENABLE EDUCATIONAL TECHNOLOGY CO., LTD.}{Taipei, Taiwan}
      \resumeItemListStart
        \resumeItem{Developed games using the Cocos Creator engine, including the Motivational Farm Reading Garden project.}
        \resumeItem{Developed 3D and VR games using the Unity engine for projects such as Fun iPlay and VR applications.}
        \resumeItem{Created games with the Phaser engine, including The Rise of Hero project.}
        \resumeItem{Built front-end interfaces for The Rise of Hero using the Vue.js}
      \resumeItemListEnd

    \resumeSubheading
      {Firmware Engineer}{Sep. 2018 -- Jan. 2021}
      {DediProg Technology}{Taipei, Taiwan}
      \resumeItemListStart
        \resumeItem{Develop and test programs using the C programming language.}
        \resumeItem{Work with MCU (Microcontroller Unit) functionalities and debugging tools.}
        \resumeItem{Conduct IC verification and develop firmware, libraries, or application platforms.}
        \resumeItem{Design electronic circuits.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Open Source Involvement}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Gravitino Contributor} $|$ \emph{\href{https://github.com/search?q=is\%3Apr+author\%3Aorenccl+repo\%3Aapache\%2Fgravitino+\&type=pullrequests}{\textcolor{blue}{View My Contributions}}}}{Nov. 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Implemented server information display functionality in CLI tool for enhanced accessibility.}
            \resumeItem{Developed an intuitive web UI to facilitate relational table creation, improving user interaction.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Gravitino Playground Contributor} $|$ \emph{\href{https://github.com/search?q=is\%3Apr+author\%3Aorenccl+repo\%3Aapache\%2Fgravitino-playground+\&type=pullrequests}{\textcolor{blue}{View My Contributions}}}}{Nov. 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Integrated Prometheus and Grafana for comprehensive monitoring through Docker containerization.}
            \resumeItem{Enhanced startup script for automated runtime and command version selection, optimizing setup efficiency.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
